%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Senior Firmware Engineer} % Job title
{Code Corporation} % Organization
{Murray, UT} % Location
{May 2019 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Firmware development is no longer the bottleneck in a product's engineering process.
\item Reduced code size by over 600\% through the combination of 8 different repositories.
\item Eliminated several days in the release process by automatically generating product documentation directly from the code.
\item Became the primary contact for firmware development and debugging in an 11-person team.
\item Reduced bug count by 85\% through unit test and custom test framework integration.
\item Led the firmware development on 3 different products where development was finished weeks prior to deadline.
\item Implemented image processing algorithms for machine vision applications for 4 different OEM customers.
\item Doubled the size and efficacy of the firmware team by creating a scalable git development process.
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Firmware Engineer} % Job title
{Code Corporation} % Organization
{Murray, UT} % Location
{May 2017 - May 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Halved product time-to-release by transitioning to an agile development environment.
\item Integrated critical wireless BLE communication systems on the highest revenue products.
\item Implemented a low-level flash file system and JavaScript interpreter, which is a critical driver for sales on flagship products.
\item Satisified all product requirements for 6 different products by developing robust drivers for low-level peripherals on a custom RTOS.
\item Fully secured our products through the design and implementation of a system which utilizes cryptographic algorithms.
\end{cvitems}
}

%------------------------------------------------

\cventry
{Firmware Engineer Intern} % Job title
{Code Corporation} % Organization
{Murray, UT} % Location
{Jan. 2017 - May 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Implemented a complete system of embedded software for a charging system.
\item Implemented communication systems for Apple MFi accessories.
\end{cvitems}
}

%------------------------------------------------

\cventry
{Teaching Assistant} % Job title
{University of Utah} % Organization
{Salt Lake City, UT} % Location
{Jan. 2016 - May. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Demonstrated proper coding and debugging techniques in 50-person laboratory exercises for low-level systems software.
\item Led a 20-person digital systems laboratory which implemented and programmed MIPS processors implemented on FPGAs.
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Northrop Grumman} % Organization
{Hill AFB, UT} % Location
{Aug. 2014 - Dec. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item \small Solved high priority requirements violations in the associated targeting sytem software and HDL.
\item \small Assisted in the implementation, documentation, and testing of operational systems for ICBM software.
\item \small Implemented a complete system of simulated in-flight targeting software.
\end{cvitems}
}

%------------------------------------------------


\cventry
{Software Engineer Intern} % Job title
{Northrop Grumman} % Organization
{Hill AFB, UT} % Location
{May 2014 - Aug. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item \small Assisted in the implementation, documentation, and testing of ground systems for ICBM software.
\end{cvitems}
}

\end{cventries}